Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-20 paper_quarto.qmd
test table
bibliography add

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of Natural History"
author: "Lizao Zhuang (Dawn) r0914937"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
code-fold: true
abstract: 'The paper applies the methodology of keyword analysis and collocation analysis in corpus linguistics to explore the possible topics of the text related to "India" in Natural History of Pliny the Elder.'
---

```{r setup, include=FALSE}
library('tidyverse')
library('mclm')
library('here')
library('kableExtra')
library('dplyr')
library('ggplot2')
library('leaflet')
options(digits = 3)
```

@@

When mapping the places with the annotated coordinates, as shown in @fig-map, India is the only one place that not in mediterranean region while having a rather high counts in the mentioned times.

@@

@@

@tbl-kwtable_PMI and @tbl-kwtable_Gsigned shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.

@@

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2^"))%>%
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

```{r}
#| label: tbl-coltable_Gsigned
#| tbl-cap-location: top
#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by G_signed)
#| warning: false
#| echo: false

@@

>>>>

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of Natural History"
author: "Lizao Zhuang (Dawn) r0914937"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
code-fold: true
bibliography:
  - bibliography.bib
  - packages.bib
csl: unified-style-sheet-for-linguistics.csl
abstract: 'The paper applies the methodology of keyword analysis and collocation analysis in corpus linguistics to explore the possible topics of the text related to "India" in Natural History of Pliny the Elder.'
---

```{r setup, include=FALSE}
library('tidyverse')
library('mclm')
library('here')
library('kableExtra')
library('dplyr')
library('ggplot2')
library('leaflet')
options(digits = 3)

knitr::write_bib(
  c("base", "mclm", "ggplot2", "tidyverse", "leaflet"),
  here("packages.bib")
)
```

@@

When mapping the places with the annotated coordinates, as shown in @fig-map, India is the only one place that not in Mediterranean region while having a rather high counts in the mentioned times.

@@

`{tidyverse}`, `{mclm}` are the main packages used in this paper.

@@

@tbl-kwtables below shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.

::: {#tbl-kwtables .panel-tabset}
## Sorted by PMI

@@

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 30 collocates to the word "india" in Natural History (sorted by PMI)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2^"))%>%
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

```{r}
#| label: tbl-coltable_Gsigned
#| tbl-cap-location: top
#| tbl-cap: Top 30 collocates to the word "india" in Natural History (sorted by G_signed)
#| warning: false
#| echo: false

@@

```{quarto-cite}
```
